Manuscript progress report

### 2024-02-06 Docs/manuscript.tex
figures and tables

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Manuscript progress report},
  pdfauthor={Ying Jin},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Manuscript progress report}
\author{Ying Jin}
\date{2023-12-06}

@@

@@

\includegraphics{manuscript_files/figure-latex/fig_sim_data-1.pdf}

\hypertarget{reference-method}{%
\subsection{Reference method}\label{reference-method}}

\begin{itemize}
\tightlist
\item
  GLMMadaptive
\item
  Here we can fit a model with random intercept and slope for time. It
  is doable on 500 datasets, but obviously too simple for the data
  generation scheme. We would expect it to perform terribly.
\end{itemize}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Manuscript progress report},
  pdfauthor={Ying Jin},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Manuscript progress report}
\author{Ying Jin}
\date{2024-02-06}

@@

\hypertarget{reference-method}{%
\section{Reference method}\label{reference-method}}

\hypertarget{glmmadaptive}{%
\subsection{GLMMadaptive}\label{glmmadaptive}}

\begin{itemize}
\tightlist
\item
  For large datasets, we can fit a model with random intercept and slope
  for time. It is doable on 500 datasets, but obviously too simple for
  the data generation scheme. We would expect it to perform terribly.
\end{itemize}

\begin{itemize}
\tightlist
\item
  For small datasets, we would like to fit fGFPCA and GLMMadaptive on a
  dataset with smaller sample size and/or smaller measurement density.
  For the GLMMadaptive model, we would set it up with spline basis
  functions so that its flexibility is comparable with fGFPCA model,
  such as:
\end{itemize}

\hypertarget{generalized-functional-on-scalar-regression}{%
\subsection{Generalized functional-on-scalar
regression}\label{generalized-functional-on-scalar-regression}}

We would like to use a second reference method for predictive
performance comparision. In this model, predictions on a specific
interval are all made using the last few observations in the observed
window. For example, if we are given observations on {[}0, 0.2{]} (j =
1\ldots200), we may use L observations taken right before t=0.2
(\(t_j: j=200, ... 200-(L-1)\)) as time-fixed covariate to predict any
future time.

Let's write out the model expression (with questionable notation). If
the observations if up to \(t_m\), then:

\[\begin{aligned}
g(E[Y_i(t)]) &= \beta_0(t) +\sum_{l=1}^L \beta_l (t)Y_i(t_l)\\
l & = m,...m-(j-1)\\
t &> t_m 
\end{aligned}\]

This is a simple function-on-scalar model with no random effect, meaning
all subject with the same last observed outcome would have the same
estimated/predicted latent track. This is clearly anti-intuitive. But
adding random effects would make out-of-sample prediction impossible.

Under both frameworks, for each dataset we need to fit four models
(similar to the GLMMadaptive method):

\begin{itemize}
\tightlist
\item
  Given 0-0.2, predict 0.2-1
\item
  Given 0-0.4, predict 0.4-1
\item
  Given 0-0.6, predict 0.6-1
\item
  Given 0-0.8, predict 0.8-1
\end{itemize}

But prediction performance will be reported by equal-length time window.

@@

\hypertarget{figures}{%
\subsection{Figures}\label{figures}}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{load}\NormalTok{(}\FunctionTok{here}\NormalTok{(}\StringTok{"Data/SimOutput\_fGFPCA.RData"}\NormalTok{))}
\FunctionTok{load}\NormalTok{(}\FunctionTok{here}\NormalTok{(}\StringTok{"Data/SimOutput\_GLMMadaptive.RData"}\NormalTok{))}
\FunctionTok{load}\NormalTok{(}\FunctionTok{here}\NormalTok{(}\StringTok{"Data/SimOutput\_GFOSR\_L1.RData"}\NormalTok{))}
\NormalTok{pred\_list\_gfosr\_l1 }\OtherTok{\textless{}{-}}\NormalTok{ pred\_list\_gfofr}
\NormalTok{t\_vec\_gfosr\_l1 }\OtherTok{\textless{}{-}}\NormalTok{ t\_vec\_gfofr}
\FunctionTok{rm}\NormalTok{(pred\_list\_gfofr, t\_vec\_gfofr)}
\FunctionTok{load}\NormalTok{(}\FunctionTok{here}\NormalTok{(}\StringTok{"Data/SimOutput\_GFOSR\_L5.RData"}\NormalTok{))}
\NormalTok{pred\_list\_gfosr\_l5 }\OtherTok{\textless{}{-}}\NormalTok{ pred\_list\_gfofr}
\NormalTok{t\_vec\_gfosr\_l5 }\OtherTok{\textless{}{-}}\NormalTok{ t\_vec\_gfofr}
\FunctionTok{rm}\NormalTok{(pred\_list\_gfofr, t\_vec\_gfofr)}

\NormalTok{rand\_id }\OtherTok{\textless{}{-}} \FunctionTok{sample}\NormalTok{(}\DecValTok{501}\SpecialCharTok{:}\DecValTok{600}\NormalTok{, }\AttributeTok{size =} \DecValTok{4}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{bind\_rows}\NormalTok{(}
\NormalTok{  pred\_list\_all[[}\DecValTok{1}\NormalTok{]] }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(id }\SpecialCharTok{\%in\%}\NormalTok{ rand\_id) }\SpecialCharTok{\%\textgreater{}\%} 
    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{method=}\StringTok{"fGFPCA"}\NormalTok{),}
\NormalTok{  pred\_list\_ref[[}\DecValTok{1}\NormalTok{]] }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(id }\SpecialCharTok{\%in\%}\NormalTok{ rand\_id) }\SpecialCharTok{\%\textgreater{}\%}
    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{method =} \StringTok{"GLMMadaptive"}\NormalTok{),}
\NormalTok{  pred\_list\_gfosr\_l1[[}\DecValTok{1}\NormalTok{]] }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(id }\SpecialCharTok{\%in\%}\NormalTok{ rand\_id) }\SpecialCharTok{\%\textgreater{}\%}
    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{method =} \StringTok{"GFOSR (L=1)"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
    \FunctionTok{rename}\NormalTok{(}\AttributeTok{pred0.2=}\NormalTok{pred\_w1, }\AttributeTok{pred0.4=}\NormalTok{pred\_w2, }\AttributeTok{pred0.6=}\NormalTok{pred\_w3, }\AttributeTok{pred0.8=}\NormalTok{pred\_w4),}
\NormalTok{  pred\_list\_gfosr\_l5[[}\DecValTok{1}\NormalTok{]] }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(id }\SpecialCharTok{\%in\%}\NormalTok{ rand\_id) }\SpecialCharTok{\%\textgreater{}\%}
    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{method =} \StringTok{"GFOSR (L=5)"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
    \FunctionTok{rename}\NormalTok{(}\AttributeTok{pred0.2=}\NormalTok{pred\_w1, }\AttributeTok{pred0.4=}\NormalTok{pred\_w2, }\AttributeTok{pred0.6=}\NormalTok{pred\_w3, }\AttributeTok{pred0.8=}\NormalTok{pred\_w4)}
\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{mutate\_at}\NormalTok{(}\FunctionTok{vars}\NormalTok{(eta\_i, pred0}\FloatTok{.2}\NormalTok{, pred0}\FloatTok{.4}\NormalTok{, pred0}\FloatTok{.6}\NormalTok{, pred0}\FloatTok{.8}\NormalTok{), }
                \AttributeTok{.funs =} \ControlFlowTok{function}\NormalTok{(x)\{}\FunctionTok{exp}\NormalTok{(x)}\SpecialCharTok{/}\NormalTok{(}\DecValTok{1}\SpecialCharTok{+}\FunctionTok{exp}\NormalTok{(x))\}) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{method=}\FunctionTok{factor}\NormalTok{(method, }
         \AttributeTok{levels =} \FunctionTok{c}\NormalTok{(}\StringTok{"fGFPCA"}\NormalTok{, }\StringTok{"GFOSR (L=5)"}\NormalTok{, }\StringTok{"GFOSR (L=1)"}\NormalTok{,}\StringTok{"GLMMadaptive"}\NormalTok{))) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{ggplot}\NormalTok{()}\SpecialCharTok{+}
  \FunctionTok{geom\_point}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x=}\NormalTok{t, }\AttributeTok{y=}\NormalTok{Y), }\AttributeTok{size =} \FloatTok{0.2}\NormalTok{)}\SpecialCharTok{+}
  \FunctionTok{geom\_line}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x=}\NormalTok{t, }\AttributeTok{y=}\NormalTok{eta\_i, }\AttributeTok{col =} \StringTok{"True"}\NormalTok{))}\SpecialCharTok{+}
  \FunctionTok{geom\_line}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x=}\NormalTok{t, }\AttributeTok{y=}\NormalTok{pred0}\FloatTok{.2}\NormalTok{, }\AttributeTok{col =} \StringTok{"0.2"}\NormalTok{), }\AttributeTok{linetype=}\StringTok{"dashed"}\NormalTok{, }\AttributeTok{na.rm=}\NormalTok{T)}\SpecialCharTok{+}
  \FunctionTok{geom\_line}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x=}\NormalTok{t, }\AttributeTok{y=}\NormalTok{pred0}\FloatTok{.4}\NormalTok{, }\AttributeTok{col =} \StringTok{"0.4"}\NormalTok{), }\AttributeTok{linetype=}\StringTok{"dashed"}\NormalTok{, }\AttributeTok{na.rm=}\NormalTok{T)}\SpecialCharTok{+}
  \FunctionTok{geom\_line}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x=}\NormalTok{t, }\AttributeTok{y=}\NormalTok{pred0}\FloatTok{.6}\NormalTok{, }\AttributeTok{col =} \StringTok{"0.6"}\NormalTok{), }\AttributeTok{linetype=}\StringTok{"dashed"}\NormalTok{, }\AttributeTok{na.rm=}\NormalTok{T)}\SpecialCharTok{+}
  \FunctionTok{geom\_line}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x=}\NormalTok{t, }\AttributeTok{y=}\NormalTok{pred0}\FloatTok{.8}\NormalTok{, }\AttributeTok{col =} \StringTok{"0.8"}\NormalTok{), }\AttributeTok{linetype=}\StringTok{"dashed"}\NormalTok{, }\AttributeTok{na.rm=}\NormalTok{T)}\SpecialCharTok{+}
  \FunctionTok{facet\_grid}\NormalTok{(}\AttributeTok{rows =} \FunctionTok{vars}\NormalTok{(id), }\AttributeTok{cols =} \FunctionTok{vars}\NormalTok{(method))}\SpecialCharTok{+}
  \FunctionTok{labs}\NormalTok{(}\AttributeTok{col =} \StringTok{"Maximum observation time"}\NormalTok{, }\AttributeTok{x =} \StringTok{"Time"}\NormalTok{, }\AttributeTok{y=}\StringTok{""}\NormalTok{)}\SpecialCharTok{+}
  \FunctionTok{scale\_x\_continuous}\NormalTok{(}\AttributeTok{breaks =} \FunctionTok{seq}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{1}\NormalTok{, }\AttributeTok{by =} \FloatTok{0.2}\NormalTok{))}\SpecialCharTok{+}
  \FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.position =} \StringTok{"bottom"}\NormalTok{)}\SpecialCharTok{+}
  \FunctionTok{scale\_color\_manual}\NormalTok{(}\AttributeTok{values =}\NormalTok{ cols)}
\end{Highlighting}
\end{Shaded}

\includegraphics{manuscript_files/figure-latex/fig_large_sim-1.pdf}

\hypertarget{ise-and-auc}{%
\subsection{ISE and AUC}\label{ise-and-auc}}

\begin{Shaded}
\begin{Highlighting}[]
\DocumentationTok{\#\# ISE container }
\NormalTok{ise\_fgfpca }\OtherTok{\textless{}{-}}\NormalTok{ ise\_adglmm }\OtherTok{\textless{}{-}}\NormalTok{ ise\_gfosr\_l1 }\OtherTok{\textless{}{-}}\NormalTok{ ise\_gfosr\_l5 }\OtherTok{\textless{}{-}} 
  \FunctionTok{array}\NormalTok{(}\ConstantTok{NA}\NormalTok{, }\AttributeTok{dim =} \FunctionTok{c}\NormalTok{(}\FunctionTok{length}\NormalTok{(window)}\SpecialCharTok{{-}}\DecValTok{2}\NormalTok{, }\FunctionTok{length}\NormalTok{(window)}\SpecialCharTok{{-}}\DecValTok{2}\NormalTok{, M))}
\CommentTok{\# dims: prediction window, max obs time, simulation iter}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\DocumentationTok{\#\# calculation}
\ControlFlowTok{for}\NormalTok{(m }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\NormalTok{M)\{}
  \CommentTok{\# this\_df \textless{}{-} pred\_list\_all[[m]]}
\NormalTok{  ise\_tb }\OtherTok{\textless{}{-}}\NormalTok{ pred\_list\_all[[m]] }\SpecialCharTok{\%\textgreater{}\%}
    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{err1 =}\NormalTok{ (pred0}\FloatTok{.2}\SpecialCharTok{{-}}\NormalTok{eta\_i)}\SpecialCharTok{\^{}}\DecValTok{2}\NormalTok{,}
           \AttributeTok{err2 =}\NormalTok{ (pred0}\FloatTok{.4}\SpecialCharTok{{-}}\NormalTok{eta\_i)}\SpecialCharTok{\^{}}\DecValTok{2}\NormalTok{,}
           \AttributeTok{err3 =}\NormalTok{ (pred0}\FloatTok{.6}\SpecialCharTok{{-}}\NormalTok{eta\_i)}\SpecialCharTok{\^{}}\DecValTok{2}\NormalTok{,}
           \AttributeTok{err4 =}\NormalTok{ (pred0}\FloatTok{.8}\SpecialCharTok{{-}}\NormalTok{eta\_i)}\SpecialCharTok{\^{}}\DecValTok{2}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
    \FunctionTok{select}\NormalTok{(id, t, }\FunctionTok{starts\_with}\NormalTok{(}\StringTok{"err"}\NormalTok{)) }\SpecialCharTok{\%\textgreater{}\%} 
    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{window =} \FunctionTok{cut}\NormalTok{(t, }\AttributeTok{breaks =}\NormalTok{ window, }\AttributeTok{include.lowest =}\NormalTok{ T)) }\SpecialCharTok{\%\textgreater{}\%} 
    \FunctionTok{group\_by}\NormalTok{(window, id) }\SpecialCharTok{\%\textgreater{}\%} 
    \FunctionTok{summarise\_at}\NormalTok{(}\FunctionTok{vars}\NormalTok{(err1, err2, err3, err4), sum) }\SpecialCharTok{\%\textgreater{}\%} 
    \FunctionTok{group\_by}\NormalTok{(window) }\SpecialCharTok{\%\textgreater{}\%} 
    \FunctionTok{summarize\_at}\NormalTok{(}\FunctionTok{vars}\NormalTok{(err1, err2, err3, err4), mean) }\SpecialCharTok{\%\textgreater{}\%}
    \FunctionTok{filter}\NormalTok{(window }\SpecialCharTok{!=} \StringTok{"[0,0.2]"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
    \FunctionTok{select}\NormalTok{(}\FunctionTok{starts\_with}\NormalTok{(}\StringTok{"err"}\NormalTok{))}
\NormalTok{  ise\_fgfpca[, ,m] }\OtherTok{\textless{}{-}} \FunctionTok{as.matrix}\NormalTok{(ise\_tb)}

\NormalTok{\}}

\NormalTok{mean\_ise\_fgfpca }\OtherTok{\textless{}{-}} \FunctionTok{apply}\NormalTok{(ise\_fgfpca, }\FunctionTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{, }\DecValTok{2}\NormalTok{), mean)}

\CommentTok{\# mean\_ise \textless{}{-} data.frame(mean\_ise) \%\textgreater{}\%}
\CommentTok{\#   mutate(Window = c("(0.2, 0.4]", "(0.4, 0.6]", "(0.6, 0.8]", "(0.8, 1.0]"),}
\CommentTok{\#          .before = 1)}
\FunctionTok{colnames}\NormalTok{(mean\_ise\_fgfpca) }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"0.2"}\NormalTok{, }\StringTok{"0.4"}\NormalTok{, }\StringTok{"0.6"}\NormalTok{, }\StringTok{"0.8"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\DocumentationTok{\#\# calculation}
\ControlFlowTok{for}\NormalTok{(m }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\NormalTok{M)\{}
  \CommentTok{\# this\_df \textless{}{-} pred\_list\_gfosr\_l1[[m]]}
\NormalTok{  ise\_tb }\OtherTok{\textless{}{-}}\NormalTok{ pred\_list\_ref[[m]] }\SpecialCharTok{\%\textgreater{}\%}
    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{err1 =}\NormalTok{ (pred0}\FloatTok{.2}\SpecialCharTok{{-}}\NormalTok{eta\_i)}\SpecialCharTok{\^{}}\DecValTok{2}\NormalTok{,}
           \AttributeTok{err2 =}\NormalTok{ (pred0}\FloatTok{.4}\SpecialCharTok{{-}}\NormalTok{eta\_i)}\SpecialCharTok{\^{}}\DecValTok{2}\NormalTok{,}
           \AttributeTok{err3 =}\NormalTok{ (pred0}\FloatTok{.6}\SpecialCharTok{{-}}\NormalTok{eta\_i)}\SpecialCharTok{\^{}}\DecValTok{2}\NormalTok{,}
           \AttributeTok{err4 =}\NormalTok{ (pred0}\FloatTok{.8}\SpecialCharTok{{-}}\NormalTok{eta\_i)}\SpecialCharTok{\^{}}\DecValTok{2}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
    \FunctionTok{select}\NormalTok{(id, t, }\FunctionTok{starts\_with}\NormalTok{(}\StringTok{"err"}\NormalTok{)) }\SpecialCharTok{\%\textgreater{}\%} 
    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{window =} \FunctionTok{cut}\NormalTok{(t, }\AttributeTok{breaks =}\NormalTok{ window, }\AttributeTok{include.lowest =}\NormalTok{ T)) }\SpecialCharTok{\%\textgreater{}\%} 
    \FunctionTok{group\_by}\NormalTok{(window, id) }\SpecialCharTok{\%\textgreater{}\%} 
    \FunctionTok{summarise\_at}\NormalTok{(}\FunctionTok{vars}\NormalTok{(err1, err2, err3, err4), sum) }\SpecialCharTok{\%\textgreater{}\%} 
    \FunctionTok{group\_by}\NormalTok{(window) }\SpecialCharTok{\%\textgreater{}\%} 
    \FunctionTok{summarize\_at}\NormalTok{(}\FunctionTok{vars}\NormalTok{(err1, err2, err3, err4), mean) }\SpecialCharTok{\%\textgreater{}\%}
    \FunctionTok{filter}\NormalTok{(window }\SpecialCharTok{!=} \StringTok{"[0,0.2]"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
    \FunctionTok{select}\NormalTok{(}\FunctionTok{starts\_with}\NormalTok{(}\StringTok{"err"}\NormalTok{))}
\NormalTok{  ise\_adglmm[, ,m] }\OtherTok{\textless{}{-}} \FunctionTok{as.matrix}\NormalTok{(ise\_tb)}
\NormalTok{\}}

\NormalTok{mean\_ise\_adglmm }\OtherTok{\textless{}{-}} \FunctionTok{apply}\NormalTok{(ise\_adglmm, }\FunctionTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{, }\DecValTok{2}\NormalTok{), mean)}
\FunctionTok{colnames}\NormalTok{(mean\_ise\_adglmm) }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"0.2"}\NormalTok{, }\StringTok{"0.4"}\NormalTok{, }\StringTok{"0.6"}\NormalTok{, }\StringTok{"0.8"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\DocumentationTok{\#\# calculation}
\ControlFlowTok{for}\NormalTok{(m }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\NormalTok{M)\{}
  \CommentTok{\# this\_df \textless{}{-} pred\_list\_ref[[m]]}
\NormalTok{  ise\_tb }\OtherTok{\textless{}{-}}\NormalTok{ pred\_list\_gfosr\_l1[[m]] }\SpecialCharTok{\%\textgreater{}\%}
    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{err1 =}\NormalTok{ (pred\_w1}\SpecialCharTok{{-}}\NormalTok{eta\_i)}\SpecialCharTok{\^{}}\DecValTok{2}\NormalTok{,}
           \AttributeTok{err2 =}\NormalTok{ (pred\_w2}\SpecialCharTok{{-}}\NormalTok{eta\_i)}\SpecialCharTok{\^{}}\DecValTok{2}\NormalTok{,}
           \AttributeTok{err3 =}\NormalTok{ (pred\_w3}\SpecialCharTok{{-}}\NormalTok{eta\_i)}\SpecialCharTok{\^{}}\DecValTok{2}\NormalTok{,}
           \AttributeTok{err4 =}\NormalTok{ (pred\_w4}\SpecialCharTok{{-}}\NormalTok{eta\_i)}\SpecialCharTok{\^{}}\DecValTok{2}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
    \FunctionTok{select}\NormalTok{(id, t, }\FunctionTok{starts\_with}\NormalTok{(}\StringTok{"err"}\NormalTok{), window) }\SpecialCharTok{\%\textgreater{}\%} 
    \CommentTok{\# mutate(window = factor(window, levels = 1:5, }
    \CommentTok{\#                        labels = c("[0,0.2]", "(0.2,0.4]", "(0.4,0.6]",))) \%\textgreater{}\% }
    \FunctionTok{group\_by}\NormalTok{(window, id) }\SpecialCharTok{\%\textgreater{}\%} 
    \FunctionTok{summarise\_at}\NormalTok{(}\FunctionTok{vars}\NormalTok{(err1, err2, err3, err4), sum) }\SpecialCharTok{\%\textgreater{}\%} 
    \FunctionTok{group\_by}\NormalTok{(window) }\SpecialCharTok{\%\textgreater{}\%} 
    \FunctionTok{summarize\_at}\NormalTok{(}\FunctionTok{vars}\NormalTok{(err1, err2, err3, err4), mean) }\SpecialCharTok{\%\textgreater{}\%}
    \FunctionTok{filter}\NormalTok{(window }\SpecialCharTok{!=} \DecValTok{1}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} 
    \FunctionTok{select}\NormalTok{(}\FunctionTok{starts\_with}\NormalTok{(}\StringTok{"err"}\NormalTok{))}
\NormalTok{  ise\_gfosr\_l1[, ,m] }\OtherTok{\textless{}{-}} \FunctionTok{as.matrix}\NormalTok{(ise\_tb)}
\NormalTok{\}}
